---
title: "Week 16 - Weekly Prep"
author: "Christopher Prener, Ph.D."
Date: "December 11, 2017"
output: html_notebook
---

## Introduction
This is the replication file for Week 16's weekly prep. The goal of this file is to review how to create one-way tables in `R`.

## Dependencies
This prep does not have any dependencies.

## Load Data
The data for this prep comes from the `ggplot2` package:

```{r}
library(ggplot2)
autoData <- mpg
```

## Questions
### Question 1
The following code creates a frequency table for the variable `drv`:

```{r}
table(autoData$drv)
```

We can see that the modal category is for front wheel drive vehicles.

### Question 2
The following code creates a proportional frequency table for the variable `drv`:

```{r}
prop.table(table(autoData$drv))
```

We can see that the modal category, front wheel drive vehicles, makes up 45.299% of the observations.

### Question 3
The following code creates a frequency table for the variable `cyl`:

```{r}
table(autoData$cyl)
```

We can see that the modal category is for four cylinder engines.

### Question 4
The following code creates a proportional frequency table for the variable `cyl`:

```{r}
prop.table(table(autoData$cyl))
```

We can see that the modal category, four cylinder engines, makes up 34.615% of the observations.


