---
title: "Week-16 Lab Replication"
author: "Christopher Prener, Ph.D."
date: "December 11, 2017"
output: html_notebook
---

## Introduction
This is the replication file for week 16's lab (the last lab of the semester! you made it!).

## Dependencies
This lab requires two packages (plus `stats`):

```{r}
library(dplyr)    # data wrangling
library(janitor)  # data tables
```

## Load Data
We'll use the `auto17` data from `testDriveR` for answering the lab's questions:

```{r}
library(testDriveR)
autoData <- auto17
```

## Part 1 - Data Prepartion
### Question 1
The code below creates a vector with the names of the four major German automobile manufacturers included in these data:

```{r}
germanCars <- c("BMW", "Mercedes-Benz", "Porsche", "Volkswagen Group of Amerca")
```

### Questions 2 and 3
We can reference the vector `germanCars` we created above to make a logical variable that is `TRUE` if the manufacturer is German and otherwise is `FALSE`. Note how we use in the `%in%` operator to make this happen. We'll also subset the variables to make a smaller data frame:

```{r}
autoData %>% 
  mutate(gerCars = ifelse(mfr %in% germanCars, TRUE, FALSE)) %>%
  select(id, gerCars, driveStr) -> autoSub
```

## Part 2 - Tables
### Question 4
The code below creates a nicely formatted frequency table for the logical variable created in question 2. We'll add a total row (a total column wouldn't really make sense here) and make sure the percentages are properly formatted:

```{r}
autoSub %>%
  tabyl(gerCars) %>%
  adorn_totals(where = "row") %>%
  adorn_pct_formatting(digits = 3)
```

The modal category is `FALSE`, which makes sense - the majority of vehicles sold for model year 2017 are not German vehicles. Surprisingly, however, they do make up a fifth of the vehicles on the market!

### Question 5
Next, we'll make a two-way contingency table that shows the breakdown of drivetain types by German vehicle status. We'll use row percents here, which will clarify the percent of German/non-German vehicles that have particular types of drivetrains.

```{r}
autoSub %>%
  tabyl(gerCars, driveStr) %>%
  adorn_totals(where = c("row", "col")) %>%
  adorn_percentages(denominator = "row") %>%
  adorn_pct_formatting(digits = 3) %>%
  adorn_ns(position = "front")
```

The biggest differences here, proportionally speaking, is that a much larger share of German vehicles have four-wheel drive and rear-wheel drive than non-German vehicles. 

## Part 3 - Chi-Squared
### Question 6
The code below fits a chi-squared model to our data:

```{r}
chisq.test(autoSub$gerCars, autoSub$driveStr)
```

The results of the chi-squared ($\chi^2= 119.62, df = 4, p <.001$) suggest that the variation we noted in the contingency is indeed meaningful.

### Question 7
The code below checks to see if our model above meets Cochran conditions assumption by saving the model results to an object and then extracting the expected frequencies:

```{r}
model <- chisq.test(autoSub$gerCars, autoSub$driveStr)
model$expected
```

We do not have any cells with fewer than 5 observations, so we meet Cochran's conditions.

### Question 8
Despite this, we'll fit a Fisher's Exact Test for practice:

```{r}
fisher.test(autoSub$gerCars, autoSub$driveStr, simulate.p.value = TRUE)
```

This provides us with an alternative p-value that is robust to violations of the Cochran conditions assumption for chi-squared tests.
